---
title: "Chap1_Bioinformatics"
author: "Pablo Rodríguez"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("seqinr")
setwd("~/Projects/MCPI_SEM-2/04_BIOINF/Chap1/src")
```

## DNA Sequence Statistics



```{r read_dengue, echo=FALSE}
dengue <- read.fasta(file='../data/sequence.fasta')
dengueseq <- dengue[[1]] # dataset into a vector
```

### Length of a DNA Sequence
It contains the secuence total lenght in nucelotides retrived from the DEN-1- Dengue virus genome sequence and stores it in the vector variable dengueseq to subsecuentily obtain the lenght of the genome sequence.
```{r lenght, echo=FALSE}
length(dengueseq)
```

### Base composition of a DNA Sequence
This will count the number of occurences of the four different nucleotides (A ,..., T), this will return the number of each nucleotides.
```{r basecomposition, echo=FALSE}
table(dengueseq)
```

### GC Content of DNA
GC: Genome secuencen GC content, is the fraction of the sequence that consist of Gs and Cs.

This metric can be calculated as the percentage of the bases in the genome that are Gs or Cs. The formula used is the following:

$GC = \frac{(G_t + C_t)*100}{len(genome)}$

```{r gc_content, echo=FALSE}
GC(dengueseq)*100
```


### 
